Gelation as a condensation frustrated by hydrodynamics and mechanical tension

### 2014-08-20 generate.tex
fig:cell_vs_cap - Redesign cell sketch with relative coordinates, use foreach and random points for salt - Phase diagram in linear scale (duh!) with only spinodal, gel, fluid and clusters

\usepackage{pgfplots}
\usepgfplotslibrary{external}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{units}
\usepgflibrary{decorations.shapes, decorations.fractals}
\usetikzlibrary{positioning, plotmarks, matrix}
\tikzexternalize
%\tikzset{external/force remake}
\tikzset{every mark/.append style={scale=0.8}}
\pgfplotsset{every axis/.append style={small}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.9}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{external}
\tikzexternalize
\tikzsetexternalprefix{figs/}

@@

\begin{figure}
	\tikzset{external/force remake}
	\tikzsetnextfilename{hydro}
	\begin{tikzpicture}[lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries}]
		\begin{groupplot}[%
			group style={
				group name=g, group size=1 by 2,
				vertical sep=4em,
				},
			width=\columnwidth,%
			ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
			]
			\nextgroupplot[
			height=0.8\columnwidth-1em,
			xlabel={$t/\tau_B$}, xmin=0, xmax=20,%
			ylabel={$R_g/\sigma$},
			]%
			\begin{scope}[every node/.style={inner sep=0.4em}]
				\node[circle, ball color=gray] at (axis cs:2.5,1.6) (n3_01){};
				\node[circle, ball color=gray, right=0 of n3_01] (n3_02){};
				\node[circle, ball color=gray, above right= -0.4em and +0.4em of n3_02] (n3_03){};
				\node[circle, ball color=gray] at (axis cs:4,1.4) (n3_11){};
				\node[circle, ball color=gray, below right=-0.4em and 0.4em of n3_11] (n3_12){};
				\node[circle, ball color=gray, above right= +0 and -0 of n3_12] (n3_13){};
				\node[circle, ball color=gray] at (axis cs:18,1.35) (n3_21){};
				\node[circle, ball color=gray, above right=0.3em and -0.4em of n3_21] (n3_22){};
				\node[circle, ball color=gray, right=0 of n3_21] (n3_23){};
			\end{scope}
			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{1}]{cluster_Rg_dynamics_N3.csv};
			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{2}]{cluster_Rg_dynamics_N3.csv};
			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{3}]{cluster_Rg_dynamics_N3.csv};
			\legend{All triplets, Most elongated 20\%, Most compact 20\%};

@@

		\end{groupplot}
		\node[lab] at (g c1r1.outer north west) {a};
		\node[lab] at (g c1r2.outer north west) {b};
	\end{tikzpicture}
	\caption{\textbf{Hydrodynamics} \textbf{a} Evolution of triplet radii of gyration in a non percolating sample ($\phi=4~\%$, $c_p=\SI{1}{\gram\per\litre}$). The characteristic time to reach the stable compact cluster is much longer than the Brownian time. \textbf{b} Bond angle distribution in a percolating sample ($\phi=8~\%$, $c_p=\SI{1.5}{\gram\per\litre}$) relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue). Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles. Insets sketch both cases, with present bonds drawn thick and future bonds drawn dotted.}
	\label{fig:general}
\end{figure}
\end{document}

>>>>

\usepackage{pgfplots}
\usepgfplotslibrary{external}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{units}
\usepgflibrary{decorations.shapes, decorations.fractals}
\usetikzlibrary{positioning, plotmarks, matrix, fit, shapes.geometric}
\tikzexternalize
%\tikzset{external/force remake}
\tikzset{every mark/.append style={scale=0.8}}
\pgfplotsset{every axis/.append style={small}}
\usepackage{pgfplots}
\pgfplotsset{compat=1.9}
\usepgfplotslibrary{groupplots}
\usepgfplotslibrary{external}
\tikzexternalize
\tikzsetexternalprefix{figs/}

@@

\begin{figure}
	%\tikzset{external/force remake}
	\tikzsetnextfilename{hydro}
	\begin{tikzpicture}[lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries}]
		\begin{groupplot}[%
			group style={
				group name=g, group size=1 by 2,
				vertical sep=4em,
				},
			width=\columnwidth,%
			ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
			]
			\nextgroupplot[
			height=0.8\columnwidth-1em,
			xlabel={$t/\tau_B$}, xmin=0, xmax=20,%
			ylabel={$R_g/\sigma$},
			]%
			\begin{scope}[every node/.style={inner sep=0.4em}]
				\node[circle, ball color=gray] at (axis cs:2.5,1.6) (n3_01){};
				\node[circle, ball color=gray, right=0 of n3_01] (n3_02){};
				\node[circle, ball color=gray, above right= -0.4em and +0.4em of n3_02] (n3_03){};
				\node[circle, ball color=gray] at (axis cs:4,1.4) (n3_11){};
				\node[circle, ball color=gray, below right=-0.4em and 0.4em of n3_11] (n3_12){};
				\node[circle, ball color=gray, above right= +0 and -0 of n3_12] (n3_13){};
				\node[circle, ball color=gray] at (axis cs:18,1.35) (n3_21){};
				\node[circle, ball color=gray, above right=0.3em and -0.4em of n3_21] (n3_22){};
				\node[circle, ball color=gray, right=0 of n3_21] (n3_23){};
			\end{scope}
			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{1}]{cluster_Rg_dynamics_N3.csv};
			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{2}]{cluster_Rg_dynamics_N3.csv};
			\addplot table [x expr=\thisrowno{0}*6, y expr=\thisrowno{3}]{cluster_Rg_dynamics_N3.csv};
			\legend{All triplets, Most elongated 20\%, Most compact 20\%};

@@

		\end{groupplot}
		\node[lab] at (g c1r1.outer north west) {a};
		\node[lab] at (g c1r2.outer north west) {b};
	\end{tikzpicture}
	\caption{\textbf{Hydrodynamics} \textbf{a} Evolution of triplet radii of gyration in a non percolating sample ($\phi=4~\%$, $c_p=\SI{1}{\gram\per\litre}$). The characteristic time to reach the stable compact cluster is much longer than the Brownian time. \textbf{b} Bond angle distribution in a percolating sample ($\phi=8~\%$, $c_p=\SI{1.5}{\gram\per\litre}$) relative to existing bonds (gray), to a future bond (red) or to a future bond involving an isolated particle (blue). Future bonds are shifted to smaller angles, whereas gas adsorption takes place from larger angles. Insets sketch both cases, with present bonds drawn thick and future bonds drawn dotted.}
	\label{fig:hydro}
\end{figure}

\begin{figure*}
	\tikzset{external/force remake}
	\tikzsetnextfilename{cell_vs_cap}
	\begin{tikzpicture}[
		pic3d/.style={inner sep=0}, %
		lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
		]%
		%box
		\draw[every node/.style={draw, inner sep=0, minimum width=0.01\textwidth, minimum height=0.12\textwidth, anchor=south west}] 
			node (Rrightwall) at (0, 0) {}
			node (Rleftwall) at (0.2\textwidth, 0) {}
			[every node/.append style={minimum height=0.06\textwidth}]
			node (Crightwall) at (0, 0.13\textwidth) {}
			node (Cleftwall) at (Crightwall.south -| Rleftwall.west) {}
			(Crightwall.north west) +(0,0.005\textwidth) rectangle (Cleftwall.north east);

		%filtre
		\foreach \x / \y in {0/0.23, 0.27/0.48, 0.52/0.73, 0.77/1}
			\fill[gray] ($(Rrightwall.north west)!\x!(Rleftwall.north east)$) rectangle ($(Crightwall.south west)!\y!(Cleftwall.south east)$);

		%laser
		\node[fill, green, semitransparent, isosceles triangle, anchor=apex, shape border rotate=-90, minimum width=0.08\textwidth, inner sep=0,  isosceles triangle apex angle=75] at ($(Crightwall.north east)!0.4!(Cleftwall.south west)$) (laser) {};

		%lens
		\filldraw[lightgray] (laser.right corner) arc[start angle=180,delta angle=180,x radius=0.04\textwidth, y radius=0.01\textwidth] --cycle;
		%colloids
		\begin{scope}[radius=0.008\textwidth, ball color=red!80]
			\shade(0.08\textwidth, 0.175\textwidth) circle;
			\shade(0.11\textwidth, 0.16\textwidth) circle;
			\shade(0.05\textwidth, 0.15\textwidth) circle;
			\shade(0.03\textwidth, 0.18\textwidth) circle;
			\shade(0.14\textwidth, 0.14\textwidth) circle;
			\shade(0.16\textwidth, 0.165\textwidth) circle;
		\end{scope}

		%polymers
		\foreach \x / \y in {0.06/0.1745, 0.17/0.1345, 0.172/0.14, 0.145/0.16, 0.19/0.18, 0.09/0.14, 0.03/0.15} 
			\draw[%
			gray, decoration={coil, segment length=0.0025\textwidth, amplitude=0.0025\textwidth},
			] (\x\textwidth, \y\textwidth)
			decorate{++(-0.0025\textwidth,-0.0025\textwidth) -- ++(0.0045\textwidth,0.0045\textwidth) -- ++(0,-0.0045\textwidth) -- ++(-0.005\textwidth,+0.005\textwidth) };

		%salt
		\begin{axis}[
			at={($(Rrightwall.south east)+(0.75,0.75)$)},
			width=0.19\textwidth-2*0.75,
			height=0.115\textwidth,
			axis lines=none,
			scale only axis,
			xmin=-1, xmax=1,ymin=0,ymax=1,
			]
			\addplot [blue, only marks, mark=*, samples=1000, mark size=0.75]
    {rand^2};
		\end{axis}

		%arrows
		\foreach \x in {0.25,0.5,0.75}
			\draw[blue!20,->, line width=0.005\textwidth] ++($(Rrightwall.south west)!\x!(Rleftwall.south east)$) +(0, 0.08\textwidth) -- +(0, 0.11\textwidth);

		%labels
		\begin{scope}[right, font=\footnotesize]
			\node[above right=0 of Rleftwall.south east] (Reservoir) {Reservoir};
			\node[anchor=north west] at (laser.lower side-|Reservoir.west) {Objective lens};
			\node at (Cleftwall-|Reservoir.west) (oc) {Observation cell};
			\node[anchor=base west] at (Rleftwall.north-|Reservoir.west){Filter};
			\node[above right,blue] at (Rleftwall.east-|Reservoir.west) {Salt diffusion};
			%\node[above right] at (0.21\textwidth, 0) {Reservoir};
		\end{scope}

		\node[inner sep=0pt,thick,fit=(Rrightwall) (oc) (laser)
		] (cellsketch) {};
		\node[lab, below right=0, inner sep=0] at (cellsketch.north west) {a};

		%%%%Phase diagram%%%%

		\begin{axis}[%
			at={($(cellsketch.north west)+(\textwidth,0)$)}, anchor=outer north east,%
			name={phasediag},%
			width=0.425\textwidth, height=0.3\textwidth,%
			xmin=0, xmax=40, xlabel={$\phi$}, x unit={\%},
			ymin=0.08, ymax=3.5, ylabel={$c_p$}, y unit={\si{\gram\per\litre}},%
			%ytick={0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,2}, yticklabels={0.1,0.2,,,0.5,,,,,1,2},%
			legend pos=north east,%
			legend style={font=\footnotesize},%
			only marks,%
			]%
			\addplot[sharp plot, no marks] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_sg.phd};
			%\addplot[sharp plot, no marks, dashed] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_bg.phd};
			%\addplot[sharp plot, no marks, dotted] table [x expr=100*\thisrowno{0}, y index=1] {fluidsolid_f.phd};
			%\addplot+[forget plot] table [x index=1,y index=2] {phase_diag_capillary.csv};
			\addplot table [x index=1,y index=2] {phase_diag_gel.csv};
			\addplot table [x index=1,y index=2] {phase_diag_fluid.csv};
			\addplot table [x index=1,y index=2] {phase_diag_clusters.csv};
			\legend{spinodal, gel, fluid, clusters};
			\node[circle, draw, gray] at (axis cs:7.4, 0.98) (155C) {};
			\node[draw, gray] at (axis cs:30, 1) (Cap1) {};
		\end{axis}
		\node[lab] at (phasediag.outer north west) {b};
	\end{tikzpicture}
	\caption{\textbf{Reservoir cell} \textbf{a} Sketch of our experimental setup. The observation cell contains initially colloids, polymer and no salt. \textbf{b} Phase diagram. \textbf{c-e} Comparison between gels made at the same state point ($\phi=27~\%$, $c_p=\SI{0.75}{\gram\per\litre}$) either in situ (\textbf{c}, blue) or ex situ (\textbf{d}, red).}
	\label{fig:cell_vs_cap}
\end{figure*}
\end{document}
